<!-- Copyright (C) 2017 Diana Corbacho

    This program is free software: you can redistribute it and/or modify
    it under the terms of the GNU General Public License as published by
    the Free Software Foundation, either version 3 of the License, or
    (at your option) any later version.

    This program is distributed in the hope that it will be useful,
    but WITHOUT ANY WARRANTY; without even the implied warranty of
    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
    GNU General Public License for more details.

    You should have received a copy of the GNU General Public License
    along with this program.  If not, see <http://www.gnu.org/licenses/>. -->
---
title: "The name of your bat group"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

# Field survey report
```{r, echo=FALSE, include=FALSE}
require(knitr)
require(ggplot2)
require(scales)

library(plyr)
library(ggplot2)

field_records <- "/path/to/csv/field/records"
all_sites <- "/path/to/sites/info"

data <- read.csv(field_records, stringsAsFactors=FALSE)
sites <- read.csv(all_sites, stringsAsFactors=FALSE)
locations <- levels(data$Location)
sessions <- unique(data[,c("Date", "Location")])
rownames(sessions) <- NULL
dates <- sort(as.Date(sessions$Date, format="%d/%m/%Y"))

data <- data[!data$Species=="",]
data$Species <- as.factor(trimws(data$Species))
data$Location <- as.factor(trimws(data$Location))
data$Sex <- as.factor(trimws(data$Sex))

# List of UK species and their full latin names
col.names <- c("B.b", "E.s", "M.be", "M.d", "M.m", "M.n", "Pl.aur", "P.pip", "P.pyg", "R.f", "R.h", "Pl.aus", "N.n", "N.l", "P.n", "M.b")
latin <- c("Barbastella barbastellus", "Eptesicus serotinus", "Myotis bechsteinii", "Myotis daubentonii", "Myotis mystacinus", "Myotis nattereri", "Plecotus auritus", "Pipistrellus pipistrellus", "Pipistrellus pygmaeus", "Rhinolophus ferrumequinum", "Rhinolophus hipposideros", "Plecotus austriacus", "Nyctalus noctula", "Nyctalus leisleri", "Pipistrellus nathusii", "Myotis brandtii")

species_df <- data.frame(matrix(latin, nrow=1, ncol=16), stringsAsFactors=FALSE)
colnames(species_df) <- col.names
```
There were `r nrow(sessions)` trapping sessions in `r length(locations)` different locations between `r format(dates[[1]],format="%d/%b/%Y")` and `r format(dates[[length(dates)]],format="%d/%b/%Y")`. A total of `r nrow(data)` bats of `r length(summary(data$Species))` different species were captured.

```{r, echo=FALSE}
# Table listing all the sessions and locations
fmt_sessions <- merge(sessions, sites)[, c("Date", "Longname", "Gr")]
colnames(fmt_sessions) <- c("Date", "Location", "Grid reference")
fmt_sessions <- fmt_sessions[order(as.Date(fmt_sessions$Date, format="%d/%m/%Y")),]
rownames(fmt_sessions) <- NULL
kable(fmt_sessions)
```

```{r, echo=FALSE}
# Pie chart with distribution by species
s.species <- summary(data$Species)
pct <- round(s.species/sum(s.species)*100)
lbls <- names(s.species)
lbls <- paste(lbls, pct) 
lbls <- paste(lbls,"%",sep="")
pie(s.species, main="Distribution by species", labels=lbls, col=rainbow(length(lbls)))
```

## Trapping locations
```{r run-locations-md, include=FALSE}
out = NULL
for (location in locations) {
  out = c(out, knit_child('location.Rmd'))
}
```
`r paste(out, collapse = '\n')`

## Species
```{r run-species-md, include=FALSE}
out = NULL
species <- levels(data$Species)
for (sp in species) {
 out = c(out, knit_child('species.Rmd'))
}
```
`r paste(out, collapse = '\n')`
